---
title: "Covariate tables for QRF model selection"
author: "Bryce Oldemeyer"
date: '2022-04-21'
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  #fig.path = "../../figures/appendix/",
  dpi = 400,
  appendix = TRUE
)
```

```{r packages}
library(tidyverse)
library(minerva)
library(kableExtra)
library(pander)


# options for table formating with "kable()"
options(knitr.kable.NA = '-')

```

```{r load figure data, echo=FALSE}

load("C:/Users/bolde/Documents/Git/QRF_extrapolation/data/mic_dat_resto.rda")
load("C:/Users/bolde/Documents/Git/QRF_extrapolation/data/hab_cov_tbl_og.rda") #taken from Mike's UWW assessment
#load("C:/Users/bolde/Documents/Git/QRF_extrapolation/data/corr_df.rda") #produced by export corr_df in mine_stats.R
Dash_comp<-read.csv("C:/Users/bolde/Documents/Git/QRF_extrapolation/data/DASH_compat_cov.csv") # discussed and identified with MA,MR,BO

mic_dat_resto = mic_dat_resto %>%
  bind_rows() %>%
  left_join(select(Dash_comp, Metric, DASH_comp), by = c("Metric")) %>%
  split(.$dataset)

```

This script is to help inform covariate selection for modifying the original QRF models. 

Starting with the current covariates included in each model.

<hr style="border:2px solid gray"> </hr>

### Original QRF Covariates

```{r cov-table}

hab_cov_tbl %>%
  select(-Covariate) %>%
  kable(booktabs = T,
        align = "ccccccccl",
        caption = "Habitat covariates and their descriptions used in each of the original QRF capacity models. Numbers indicate where each metric ranked in relative importance for each model. Dots indicate a metric was not used for a given model. Table credit: Mike Ackerman.") %>%
  kable_styling(position = "center",
                bootstrap_options = c("striped", "condensed"))

```

<hr style="border:2px solid gray"> </hr>

### Steelhead - Summer CHaMP Covariate Table


```{r mic-tab-steelhead-summer-champ}

load("C:/Users/bolde/Documents/Git/QRF_extrapolation/data/hab_cov_tbl_og.rda") #taken from Mike's UWW assessment

hab_cov_tbl = hab_cov_tbl %>%
  select(c(1,2,3,4,6,8)) %>%
  rename("MetricCategory" = `Metric Category`,
         "Summer" = `Juv Sum Chnk`,
         "Winter" = `Juv Win Chnk`,
         "Redds" = `Redds Chnk`)

mine_tab_df = mic_dat_resto$Summer_CHaMP %>%
  mutate(`Percent 0-value` = 1 - perc_non0) %>%
  arrange(desc(MIC.x)) %>%
  group_by(MetricCategory) %>%
  slice(1:10) %>%
  left_join(select(hab_cov_tbl, Name, Summer), by = "Name") %>%
  select(Category = MetricCategory,
         Name,
         Abbrv = Metric,
         MIC = MIC.x,
         `Percent missing` = perc_NA,
         `Percent 0-value`,
         `Resto inform` = RestoInform,
         `DASH comp` = DASH_comp,
         `QRF_select` = Summer)

panderOptions("graph.fontsize", 10)
mine_tab_df %>%
    select(-QRF_select) %>%
  pander(digits = 3,
         caption = 'MIC statistic for top metrics within each habitat category, sorted by category and MIC value. The percent of records that were missing or zero is shown for each habitat metric. Additionally, each covariate is designated as informative (1) or not informative (0) for restoration design. Covariates included in the original QRF models are bolded. Table format credit: Kevin See.',
           emphasize.strong.rows = which(!is.na(mine_tab_df$QRF_select)),
split.tables = Inf)

```

<hr style="border:2px solid gray"> </hr>

### Chinook - Summer CHaMP Covariate Table 

```{r mic-tab-chinook-summer-champ}
mine_tab_df = mic_dat_resto$Summer_CHaMP %>%
  mutate(`Percent 0-value` = 1 - perc_non0) %>%
  arrange(desc(MIC.y)) %>%
  group_by(MetricCategory) %>%
  slice(1:10) %>%
  left_join(select(hab_cov_tbl, Name, Summer), by = "Name") %>%
  select(Category = MetricCategory,
         Name,
         Abbrv = Metric,
         MIC = MIC.y,
         `Percent missing` = perc_NA,
         `Percent 0-value`,
         `Resto inform` = RestoInform,
         `DASH comp` = DASH_comp,
         `QRF_select` = Summer)

panderOptions("graph.fontsize", 10)
mine_tab_df %>%
    select(-QRF_select) %>%
  pander(digits = 3,
         emphasize.strong.rows = which(!is.na(mine_tab_df$QRF_select)),
split.tables = Inf)


```

<hr style="border:2px solid gray"> </hr>

### Steelhead - Summer DASH Covariate Table 

```{r mic-tab-steelhead-summer-dash}
mine_tab_df = mic_dat_resto$Summer_DASH %>%
  mutate(`Percent 0-value` = 1 - perc_non0) %>%
  arrange(desc(MIC.x)) %>%
  group_by(MetricCategory) %>%
  slice(1:10) %>%
  left_join(select(hab_cov_tbl, Name, Summer), by = "Name") %>%
  select(Category = MetricCategory,
         Name,
         Abbrv = Metric,
         MIC = MIC.x,
         `Percent missing` = perc_NA,
         `Percent 0-value`,
         `Resto inform` = RestoInform,  
         `DASH comp` = DASH_comp,
         `QRF_select` = Summer)

panderOptions("graph.fontsize", 10)
mine_tab_df %>%
    select(-QRF_select) %>%
  pander(digits = 3,
         emphasize.strong.rows = which(!is.na(mine_tab_df$QRF_select)),
split.tables = Inf)


```

<hr style="border:2px solid gray"> </hr>

### Chinook - Summer DASH Covariate Table 

```{r mic-tab-chinook-summer-dash}
mine_tab_df = mic_dat_resto$Summer_DASH %>%
  mutate(`Percent 0-value` = 1 - perc_non0) %>%
  arrange(desc(MIC.y)) %>%
  group_by(MetricCategory) %>%
  slice(1:10) %>%
  left_join(select(hab_cov_tbl, Name, Summer), by = "Name") %>%
  select(Category = MetricCategory,
         Name,
         Abbrv = Metric,
         MIC = MIC.y,
         `Percent missing` = perc_NA,
         `Percent 0-value`,
         `Resto inform` = RestoInform,
         `DASH comp` = DASH_comp,
         `QRF_select` = Summer)

panderOptions("graph.fontsize", 10)
mine_tab_df %>%
    select(-QRF_select) %>%
  pander(digits = 3,
         emphasize.strong.rows = which(!is.na(mine_tab_df$QRF_select)),
split.tables = Inf)


```

<hr style="border:2px solid gray"> </hr>

### Steelhead - Redds Covariate Table 

```{r mic-tab-steelhead-redds}
mine_tab_df = mic_dat_resto$Redds %>%
  mutate(`Percent 0-value` = 1 - perc_non0) %>%
  arrange(desc(MIC.x)) %>%
  group_by(MetricCategory) %>%
  slice(1:10) %>%
  left_join(select(hab_cov_tbl, Name, Redds), by = "Name") %>%
  select(Category = MetricCategory,
         Name,
         Abbrv = Metric,
         MIC = MIC.x,
         `Percent missing` = perc_NA,
         `Percent 0-value`,
         `Resto inform` = RestoInform,
         `DASH comp` = DASH_comp,
         `QRF_select` = Redds)

panderOptions("graph.fontsize", 10)
mine_tab_df %>%
    select(-QRF_select) %>%
  pander(digits = 3,
         emphasize.strong.rows = which(!is.na(mine_tab_df$QRF_select)),
split.tables = Inf)


```

<hr style="border:2px solid gray"> </hr>

### Chinook - Redds Covariate Table 

```{r mic-tab-chinook-redds}
mine_tab_df = mic_dat_resto$Redds %>%
  mutate(`Percent 0-value` = 1 - perc_non0) %>% 
  arrange(desc(MIC.y)) %>%
  group_by(MetricCategory) %>%
  slice(1:10) %>%
  left_join(select(hab_cov_tbl, Name, Redds), by = "Name") %>%
  select(Category = MetricCategory,
         Name,
         Abbrv = Metric,
         MIC = MIC.y,
         `Percent missing` = perc_NA,
         `Percent 0-value`,
         `Resto inform` = RestoInform,
         `DASH comp` = DASH_comp,
         `QRF_select` = Redds)

panderOptions("graph.fontsize", 10)
mine_tab_df %>%
    select(-QRF_select) %>%
  pander(digits = 3,
         emphasize.strong.rows = which(!is.na(mine_tab_df$QRF_select)),
split.tables = Inf)


```

<hr style="border:2px solid gray"> </hr>

### Steelhead - Winter Covariate Table 

```{r mic-tab-steelhead-winter}
mine_tab_df = mic_dat_resto$Winter %>%
  mutate(`Percent 0-value` = 1 - perc_non0) %>%
  arrange(desc(MIC.x)) %>%
  group_by(MetricCategory) %>%
  slice(1:10) %>%
  left_join(select(hab_cov_tbl, Name, Winter), by = "Name") %>%
  select(Category = MetricCategory,
         Name,
         Abbrv = Metric,
         MIC = MIC.x,
         `Percent missing` = perc_NA,
         `Percent 0-value`,
         `Resto inform` = RestoInform,    
         `DASH comp` = DASH_comp,
         `QRF_select` = Winter)

panderOptions("graph.fontsize", 10)
mine_tab_df %>%
    select(-QRF_select) %>%
  pander(digits = 3,
         emphasize.strong.rows = which(!is.na(mine_tab_df$QRF_select)),
split.tables = Inf)


```

<hr style="border:2px solid gray"> </hr>

### Chinook - Winter Covariate Table 

```{r mic-tab-chinook-winter}
mine_tab_df = mic_dat_resto$Winter %>%
  mutate(`Percent 0-value` = 1 - perc_non0) %>%
  arrange(desc(MIC.y)) %>%
  group_by(MetricCategory) %>%
  slice(1:10) %>%
  left_join(select(hab_cov_tbl, Name, Winter), by = "Name") %>%
  select(Category = MetricCategory,
         Name,
         Abbrv = Metric,
         MIC = MIC.y,
         `Percent missing` = perc_NA,
         `Percent 0-value`,
         `Resto inform` = RestoInform, 
         `DASH comp` = DASH_comp,
         `QRF_select` = Winter)

panderOptions("graph.fontsize", 10)
mine_tab_df %>%
    select(-QRF_select) %>%
  pander(digits = 3,
         emphasize.strong.rows = which(!is.na(mine_tab_df$QRF_select)),
split.tables = Inf)


```
