---
title: "Extrapolation model selection"
author: "Mark Roes"
date: "5/25/2022"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(quantregForest)
library(kableExtra)
library(here)


knitr::opts_chunk$set(echo = TRUE)

mod_path = 'S:/main/data/qrf/gitrepo_data/output/modelFit/'

source(here("R/plot_partial_dependence.r"))

load(here("data/gaa_hab_dict.rda"))
```

Below are summary statistics and figures for a series of extraplation models. They are: Random forest log-response, random forest non-transformed response, and GLM log-response. Summary tables are presented by CHaMP watershed, with NA representing summary statistics for all non-CHaMP watersheds.

Figures are presented for the random forest log-response model. These figures are based on the model built for extrapolation beyond CHaMP watersheds, so it does not include a watershed effect. In practice, any extrapolations made within CHaMP watersheds include a watershed effect, while extrapolations outside of these watersheds do not.

# Winter model

**RF, log-response**
```{r rf_log_win summary stats, echo = F, message = F}
mod_choice = c('juv_summer',
               'redds',
               'juv_winter')[3]

cov_choice = c("Reduced")[1]

log_mod = c("log_","")[1]

load(paste0(mod_path,"extrap_200rch_RF_",log_mod,mod_choice,'.rda'))


all_preds %<>%
  filter(chnk == TRUE | sthd == TRUE) %>%
  pivot_longer(cols = c("chnk","sthd")) 

rf_log_win_chk = all_preds %>%
  filter(name == 'chnk' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(chnk_per_m, probs = .5),
               m.se = quantile(chnk_per_m_se, probs = .5),
               p25.m = quantile(chnk_per_m, probs = .25),
               p75.m = quantile(chnk_per_m, probs = .75),
               max.m = max(chnk_per_m),
               p50.m2 = quantile(chnk_per_m2, probs = .5),
               m2.se = quantile(chnk_per_m2_se, probs = .5),
               p25.m2 = quantile(chnk_per_m2, probs = .25),
               p75.m2 = quantile(chnk_per_m2, probs = .75),
               max.m2 = max(chnk_per_m2))
  
rf_log_win_stl = all_preds %>%
  filter(name == 'sthd' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(sthd_per_m, probs = .5),
               m.se = quantile(sthd_per_m_se, probs = .5),
               p25.m = quantile(sthd_per_m, probs = .25),
               p75.m = quantile(sthd_per_m, probs = .75),
               max.m = max(sthd_per_m),
               p50.m2 = quantile(sthd_per_m2, probs = .5),
               m2.se = quantile(sthd_per_m2_se, probs = .5),
               p25.m2 = quantile(sthd_per_m2, probs = .25),
               p75.m2 = quantile(sthd_per_m2, probs = .75),
               max.m2 = max(sthd_per_m2))

kable(rf_log_win_chk, caption = "Chinook", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3 )

kable(rf_log_win_stl, caption = "Steelhead", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3)

#Figures
load(here(paste0("output/figures/","RF_extrap_", log_mod, mod_choice,'_', cov_choice,".rda")))



chk_ri
chk_m
chk_m2
stl_ri
stl_m
stl_m2

rm(model_rf_df,
   pred_hab_df,
   all_preds,
   chk_ri,
   chk_m,
   chk_m2,
   stl_ri,
   stl_m,
   stl_m2)
```

**RF, untransformed response**
```{r rf_win summary stats, echo = F}
mod_choice = c('juv_summer',
               'redds',
               'juv_winter')[3]

cov_choice = c("Reduced")[1]

log_mod = c("log_","")[2]

load(paste0(mod_path,"extrap_200rch_RF_",log_mod,mod_choice,'.rda'))

all_preds %<>%
  filter(chnk == TRUE | sthd == TRUE) %>%
  pivot_longer(cols = c("chnk","sthd")) 

rf_win_chk = all_preds %>%
  filter(name == 'chnk' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(chnk_per_m, probs = .5),
               m.se = quantile(chnk_per_m_se, probs = .5),
               p25.m = quantile(chnk_per_m, probs = .25),
               p75.m = quantile(chnk_per_m, probs = .75),
               max.m = max(chnk_per_m),
               p50.m2 = quantile(chnk_per_m2, probs = .5),
               m2.se = quantile(chnk_per_m2_se, probs = .5),
               p25.m2 = quantile(chnk_per_m2, probs = .25),
               p75.m2 = quantile(chnk_per_m2, probs = .75),
               max.m2 = max(chnk_per_m2))
  
rf_win_stl = all_preds %>%
  filter(name == 'sthd' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(sthd_per_m, probs = .5),
               m.se = quantile(sthd_per_m_se, probs = .5),
               p25.m = quantile(sthd_per_m, probs = .25),
               p75.m = quantile(sthd_per_m, probs = .75),
               max.m = max(sthd_per_m),
               p50.m2 = quantile(sthd_per_m2, probs = .5),
               m2.se = quantile(sthd_per_m2_se, probs = .5),
               p25.m2 = quantile(sthd_per_m2, probs = .25),
               p75.m2 = quantile(sthd_per_m2, probs = .75),
               max.m2 = max(sthd_per_m2))

kable(rf_log_win_chk, caption = "Chinook", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3 )

kable(rf_log_win_stl, caption = "Steelhead", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3)



```

**GLM, log-response**
```{r glm_win summary stats, echo = F}
mod_choice = c('juv_summer',
               'redds',
               'juv_winter')[3]

cov_choice = c("Reduced")[1]

load(paste0(mod_path,"extrap_200rch_",cov_choice,'_',mod_choice,'.rda'))

all_preds %<>%
  filter(chnk == TRUE | sthd == TRUE) %>%
  pivot_longer(cols = c("chnk","sthd")) 

glm_win_chk = all_preds %>%
  filter(name == 'chnk' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(chnk_per_m, probs = .5),
               m.se = quantile(chnk_per_m_se, probs = .5),
               p25.m = quantile(chnk_per_m, probs = .25),
               p75.m = quantile(chnk_per_m, probs = .75),
               max.m = max(chnk_per_m),
               p50.m2 = quantile(chnk_per_m2, probs = .5),
               m2.se = quantile(chnk_per_m2_se, probs = .5),
               p25.m2 = quantile(chnk_per_m2, probs = .25),
               p75.m2 = quantile(chnk_per_m2, probs = .75),
               max.m2 = max(chnk_per_m2))
  
glm_win_stl = all_preds %>%
  filter(name == 'sthd' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(sthd_per_m, probs = .5),
               m.se = quantile(sthd_per_m_se, probs = .5),
               p25.m = quantile(sthd_per_m, probs = .25),
               p75.m = quantile(sthd_per_m, probs = .75),
               max.m = max(sthd_per_m),
               p50.m2 = quantile(sthd_per_m2, probs = .5),
               m2.se = quantile(sthd_per_m2_se, probs = .5),
               p25.m2 = quantile(sthd_per_m2, probs = .25),
               p75.m2 = quantile(sthd_per_m2, probs = .75),
               max.m2 = max(sthd_per_m2))

kable(rf_log_win_chk, caption = "Chinook", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3 )

kable(rf_log_win_stl, caption = "Steelhead", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3)


```


# Summer model

**RF, log-response**
```{r rf_log_sum summary stats, echo = F, message = F}
mod_choice = c('juv_summer',
               'redds',
               'juv_winter')[1]

cov_choice = c("Reduced")[1]

log_mod = c("log_","")[1]

load(paste0(mod_path,"extrap_200rch_RF_",log_mod,mod_choice,'.rda'))


all_preds %<>%
  filter(chnk == TRUE | sthd == TRUE) %>%
  pivot_longer(cols = c("chnk","sthd")) 

rf_log_sum_chk = all_preds %>%
  filter(name == 'chnk' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(chnk_per_m, probs = .5),
               m.se = quantile(chnk_per_m_se, probs = .5),
               p25.m = quantile(chnk_per_m, probs = .25),
               p75.m = quantile(chnk_per_m, probs = .75),
               max.m = max(chnk_per_m),
               p50.m2 = quantile(chnk_per_m2, probs = .5),
               m2.se = quantile(chnk_per_m2_se, probs = .5),
               p25.m2 = quantile(chnk_per_m2, probs = .25),
               p75.m2 = quantile(chnk_per_m2, probs = .75),
               max.m2 = max(chnk_per_m2))
  
rf_log_sum_stl = all_preds %>%
  filter(name == 'sthd' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(sthd_per_m, probs = .5),
               m.se = quantile(sthd_per_m_se, probs = .5),
               p25.m = quantile(sthd_per_m, probs = .25),
               p75.m = quantile(sthd_per_m, probs = .75),
               max.m = max(sthd_per_m),
               p50.m2 = quantile(sthd_per_m2, probs = .5),
               m2.se = quantile(sthd_per_m2_se, probs = .5),
               p25.m2 = quantile(sthd_per_m2, probs = .25),
               p75.m2 = quantile(sthd_per_m2, probs = .75),
               max.m2 = max(sthd_per_m2))

kable(rf_log_sum_chk, caption = "Chinook", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3 )

kable(rf_log_sum_stl, caption = "Steelhead", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3)

#Figures
load(here(paste0("output/figures/","RF_extrap_", log_mod, mod_choice,'_', cov_choice,".rda")))



chk_ri
chk_m
chk_m2
stl_ri
stl_m
stl_m2

rm(model_rf_df,
   pred_hab_df,
   all_preds,
   chk_ri,
   chk_m,
   chk_m2,
   stl_ri,
   stl_m,
   stl_m2)
```

**RF, untransformed response**
```{r rf_sum summary stats, echo = F}
mod_choice = c('juv_summer',
               'redds',
               'juv_winter')[1]

cov_choice = c("Reduced")[1]

log_mod = c("log_","")[2]

load(paste0(mod_path,"extrap_200rch_RF_",log_mod,mod_choice,'.rda'))

all_preds %<>%
  filter(chnk == TRUE | sthd == TRUE) %>%
  pivot_longer(cols = c("chnk","sthd")) 

rf_sum_chk = all_preds %>%
  filter(name == 'chnk' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(chnk_per_m, probs = .5),
               m.se = quantile(chnk_per_m_se, probs = .5),
               p25.m = quantile(chnk_per_m, probs = .25),
               p75.m = quantile(chnk_per_m, probs = .75),
               max.m = max(chnk_per_m),
               p50.m2 = quantile(chnk_per_m2, probs = .5),
               m2.se = quantile(chnk_per_m2_se, probs = .5),
               p25.m2 = quantile(chnk_per_m2, probs = .25),
               p75.m2 = quantile(chnk_per_m2, probs = .75),
               max.m2 = max(chnk_per_m2))
  
rf_sum_stl = all_preds %>%
  filter(name == 'sthd' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(sthd_per_m, probs = .5),
               m.se = quantile(sthd_per_m_se, probs = .5),
               p25.m = quantile(sthd_per_m, probs = .25),
               p75.m = quantile(sthd_per_m, probs = .75),
               max.m = max(sthd_per_m),
               p50.m2 = quantile(sthd_per_m2, probs = .5),
               m2.se = quantile(sthd_per_m2_se, probs = .5),
               p25.m2 = quantile(sthd_per_m2, probs = .25),
               p75.m2 = quantile(sthd_per_m2, probs = .75),
               max.m2 = max(sthd_per_m2))

kable(rf_sum_chk, caption = "Chinook", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3 )

kable(rf_sum_stl, caption = "Steelhead", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3)

```

**GLM, log-response**
```{r glm_sum summary stats, echo = F}
mod_choice = c('juv_summer',
               'redds',
               'juv_winter')[1]

cov_choice = c("Reduced")[1]

load(paste0(mod_path,"extrap_200rch_",cov_choice,'_',mod_choice,'.rda'))

all_preds %<>%
  filter(chnk == TRUE | sthd == TRUE) %>%
  pivot_longer(cols = c("chnk","sthd")) 

glm_sum_chk = all_preds %>%
  filter(name == 'chnk' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(chnk_per_m, probs = .5),
               m.se = quantile(chnk_per_m_se, probs = .5),
               p25.m = quantile(chnk_per_m, probs = .25),
               p75.m = quantile(chnk_per_m, probs = .75),
               max.m = max(chnk_per_m),
               p50.m2 = quantile(chnk_per_m2, probs = .5),
               m2.se = quantile(chnk_per_m2_se, probs = .5),
               p25.m2 = quantile(chnk_per_m2, probs = .25),
               p75.m2 = quantile(chnk_per_m2, probs = .75),
               max.m2 = max(chnk_per_m2))
  
glm_sum_stl = all_preds %>%
  filter(name == 'sthd' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.m = quantile(sthd_per_m, probs = .5),
               m.se = quantile(sthd_per_m_se, probs = .5),
               p25.m = quantile(sthd_per_m, probs = .25),
               p75.m = quantile(sthd_per_m, probs = .75),
               max.m = max(sthd_per_m),
               p50.m2 = quantile(sthd_per_m2, probs = .5),
               m2.se = quantile(sthd_per_m2_se, probs = .5),
               p25.m2 = quantile(sthd_per_m2, probs = .25),
               p75.m2 = quantile(sthd_per_m2, probs = .75),
               max.m2 = max(sthd_per_m2))

kable(glm_sum_chk, caption = "Chinook", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3 )

kable(glm_sum_stl, caption = "Steelhead", col.names = c("Watershed", "Median per m", "Per m SE", "Q25 per m", "Q75 per m", "Max per m","Median per m2", "Per m2 SE", "Q25 per m2", "Q75 per m2", "Max per m2"), digits = 3)

```

# Redd model

**RF, log-response**
```{r rf_log_redd summary stats, echo = F, message = F}
mod_choice = c('juv_summer',
               'redds',
               'juv_winter')[2]

cov_choice = c("Reduced")[1]

log_mod = c("log_","")[1]

load(paste0(mod_path,"extrap_200rch_RF_",log_mod,mod_choice,'.rda'))


all_preds %<>%
  filter(chnk == TRUE | sthd == TRUE) %>%
  pivot_longer(cols = c("chnk","sthd")) 

rf_log_redd_chk = all_preds %>%
  filter(name == 'chnk' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.km = quantile(chnk_per_m, probs = .5)*1000,
               km.se = quantile(chnk_per_m_se, probs = .5)*1000,
               p25.km = quantile(chnk_per_m, probs = .25)*1000,
               p75.km = quantile(chnk_per_m, probs = .75)*1000,
               max.km = max(chnk_per_m)*1000,
               p50.km2 = quantile(chnk_per_m2, probs = .5)*1000,
               km2.se = quantile(chnk_per_m2_se, probs = .5)*1000,
               p25.km2 = quantile(chnk_per_m2, probs = .25)*1000,
               p75.km2 = quantile(chnk_per_m2, probs = .75)*1000,
               max.km2 = max(chnk_per_m2)*1000)
  
rf_log_redd_stl = all_preds %>%
  filter(name == 'sthd' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.km = quantile(sthd_per_m, probs = .5)*1000,
               km.se = quantile(sthd_per_m_se, probs = .5)*1000,
               p25.km = quantile(sthd_per_m, probs = .25)*1000,
               p75.km = quantile(sthd_per_m, probs = .75)*1000,
               max.km = max(sthd_per_m)*1000,
               p50.km2 = quantile(sthd_per_m2, probs = .5)*1000,
               km2.se = quantile(sthd_per_m2_se, probs = .5)*1000,
               p25.km2 = quantile(sthd_per_m2, probs = .25)*1000,
               p75.km2 = quantile(sthd_per_m2, probs = .75)*1000,
               max.km2 = max(sthd_per_m2)*1000)

kable(rf_log_redd_chk, caption = "Chinook", col.names = c("Watershed", "Median per km", "Per km SE", "Q25 per km", "Q75 per km", "Max per km","Median per km2", "Per km2 SE", "Q25 per km2", "Q75 per km2", "Max per km2"), digits = 3 )

kable(rf_log_redd_stl, caption = "Steelhead", col.names = c("Watershed", "Median per km", "Per km SE", "Q25 per km", "Q75 per km", "Max per km","Median per km2", "Per km2 SE", "Q25 per km2", "Q75 per km2", "Max per km2"), digits = 3)

#Figures
load(here(paste0("output/figures/","RF_extrap_", log_mod, mod_choice,'_', cov_choice,".rda")))



chk_ri
chk_m
chk_m2
stl_ri
stl_m
stl_m2

rm(model_rf_df,
   pred_hab_df,
   all_preds,
   chk_ri,
   chk_m,
   chk_m2,
   stl_ri,
   stl_m,
   stl_m2)
```

**RF, untransformed response**
```{r rf_redd summary stats, echo = F}
mod_choice = c('juv_summer',
               'redds',
               'juv_winter')[2]

cov_choice = c("Reduced")[1]

log_mod = c("log_","")[2]

load(paste0(mod_path,"extrap_200rch_RF_",log_mod,mod_choice,'.rda'))

all_preds %<>%
  filter(chnk == TRUE | sthd == TRUE) %>%
  pivot_longer(cols = c("chnk","sthd")) 

rf_redd_chk = all_preds %>%
  filter(name == 'chnk' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.km = quantile(chnk_per_m, probs = .5)*1000,
               km.se = quantile(chnk_per_m_se, probs = .5)*1000,
               p25.km = quantile(chnk_per_m, probs = .25)*1000,
               p75.km = quantile(chnk_per_m, probs = .75)*1000,
               max.km = max(chnk_per_m)*1000,
               p50.km2 = quantile(chnk_per_m2, probs = .5)*1000,
               km2.se = quantile(chnk_per_m2_se, probs = .5)*1000,
               p25.km2 = quantile(chnk_per_m2, probs = .25)*1000,
               p75.km2 = quantile(chnk_per_m2, probs = .75)*1000,
               max.km2 = max(chnk_per_m2)*1000)
  
rf_redd_stl = all_preds %>%
  filter(name == 'sthd' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.km = quantile(sthd_per_m, probs = .5)*1000,
               km.se = quantile(sthd_per_m_se, probs = .5)*1000,
               p25.km = quantile(sthd_per_m, probs = .25)*1000,
               p75.km = quantile(sthd_per_m, probs = .75)*1000,
               max.km = max(sthd_per_m)*1000,
               p50.km2 = quantile(sthd_per_m2, probs = .5)*1000,
               km2.se = quantile(sthd_per_m2_se, probs = .5)*1000,
               p25.km2 = quantile(sthd_per_m2, probs = .25)*1000,
               p75.km2 = quantile(sthd_per_m2, probs = .75)*1000,
               max.km2 = max(sthd_per_m2)*1000)

kable(rf_redd_chk, caption = "Chinook", col.names = c("Watershed", "Median per km", "Per km SE", "Q25 per km", "Q75 per km", "Max per km","Median per km2", "Per km2 SE", "Q25 per km2", "Q75 per km2", "Max per km2"), digits = 3 )

kable(rf_redd_stl, caption = "Steelhead", col.names = c("Watershed", "Median per km", "Per km SE", "Q25 per km", "Q75 per km", "Max per km","Median per km2", "Per km2 SE", "Q25 per km2", "Q75 per km2", "Max per km2"), digits = 3)

```

**GLM, log-response**
```{r glm_redd summary stats, echo = F}
mod_choice = c('juv_summer',
               'redds',
               'juv_winter')[2]

cov_choice = c("Reduced")[1]

load(paste0(mod_path,"extrap_200rch_",cov_choice,'_',mod_choice,'.rda'))

all_preds %<>%
  filter(chnk == TRUE | sthd == TRUE) %>%
  pivot_longer(cols = c("chnk","sthd")) 

glm_redd_chk = all_preds %>%
  filter(name == 'chnk' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.km = quantile(chnk_per_m, probs = .5)*1000,
               km.se = quantile(chnk_per_m_se, probs = .5)*1000,
               p25.km = quantile(chnk_per_m, probs = .25)*1000,
               p75.km = quantile(chnk_per_m, probs = .75)*1000,
               max.km = max(chnk_per_m)*1000,
               p50.km2 = quantile(chnk_per_m2, probs = .5)*1000,
               km2.se = quantile(chnk_per_m2_se, probs = .5)*1000,
               p25.km2 = quantile(chnk_per_m2, probs = .25)*1000,
               p75.km2 = quantile(chnk_per_m2, probs = .75)*1000,
               max.km2 = max(chnk_per_m2)*1000)
  
glm_redd_stl = all_preds %>%
  filter(name == 'sthd' & value == TRUE) %>%
  group_by(Watershed) %>%
summarise(p50.km = quantile(sthd_per_m, probs = .5)*1000,
               km.se = quantile(sthd_per_m_se, probs = .5)*1000,
               p25.km = quantile(sthd_per_m, probs = .25)*1000,
               p75.km = quantile(sthd_per_m, probs = .75)*1000,
               max.km = max(sthd_per_m)*1000,
               p50.km2 = quantile(sthd_per_m2, probs = .5)*1000,
               km2.se = quantile(sthd_per_m2_se, probs = .5)*1000,
               p25.km2 = quantile(sthd_per_m2, probs = .25)*1000,
               p75.km2 = quantile(sthd_per_m2, probs = .75)*1000,
               max.km2 = max(sthd_per_m2)*1000)

kable(glm_redd_chk, caption = "Chinook", col.names = c("Watershed", "Median per km", "Per km SE", "Q25 per km", "Q75 per km", "Max per km","Median per km2", "Per km2 SE", "Q25 per km2", "Q75 per km2", "Max per km2"), digits = 3 )

kable(glm_redd_stl, caption = "Steelhead", col.names = c("Watershed", "Median per km", "Per km SE", "Q25 per km", "Q75 per km", "Max per km","Median per km2", "Per km2 SE", "Q25 per km2", "Q75 per km2", "Max per km2"), digits = 3)

```

